noam_data_exploration_v1

### 2024-07-16 noam_data_exploration_v3.Rmd
Added codyn measure of community stability, which is similar to how other papers (including Pete's) has defined portfolio effects. This is just 1/CV.

alpha_diversity$Cover <- rowSums(wide_transect_level[5:74])/100

diversity_stability <- alpha_diversity %>%
  dplyr::group_by(Site, Habitat, Site_habitat, Transect) %>%
  dplyr::summarise(Richness_mean = mean(Richness), 
            Richness_se = sd(Richness)/sqrt(n()),
            Richness_cv = CV(Richness),
            Shannon_mean = mean(Shannon), 
            Shannon_se = sd(Shannon)/sqrt(n()),
            Shannon_cv = CV(Shannon),
            Cover_mean = mean(Cover),
            Cover_se = sd(Cover)/sqrt(n()),
            Cover_cv = CV(Cover))

>>>>

alpha_diversity$Cover <- rowSums(wide_transect_level[ , -which(names(wide_transect_level) %in% meta_cols)])/100
alpha_diversity$Stratum <- paste(alpha_diversity$Site, "-", alpha_diversity$Habitat, "-", alpha_diversity$Transect)

diversity_stability <- alpha_diversity %>%
  dplyr::group_by(Site, Habitat, Site_habitat, Transect, Stratum) %>%
  dplyr::summarise(Richness_mean = mean(Richness), 
            Richness_se = sd(Richness)/sqrt(n()),
            Richness_cv = CV(Richness),
            Shannon_mean = mean(Shannon), 
            Shannon_se = sd(Shannon)/sqrt(n()),
            Shannon_cv = CV(Shannon),
            Cover_mean = mean(Cover),
            Cover_se = sd(Cover)/sqrt(n()),
            Cover_cv = CV(Cover))
stability_transect <- community_stability(df = transect_level,
                                          time.var = "Year",
                                          abundance.var = "Mean_cover",
                                          replicate.var = "Stratum") # using codyn measure of stability
# NOTE: codyn community_stability() is just the inverse of CV
diversity_stability <- merge(diversity_stability, stability_transect, by = "Stratum")
library(ecofolio) # possible other method for examining portfolio effects
